---
title: "Homework 5"
author: "Laura Cosgrove"
date: "11/3/2018"
output: github_document
---

## Problem 1
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r packages}
library(tidyverse)
```

```{r}

directory_base <- "./data/"
study_data <- tibble(files = str_c(directory_base, list.files("./data")))

study_data <- study_data %>% 
  mutate(subject_data = map(study_data$files, read_csv)) %>% 
  unnest() %>% 
  mutate(files = str_replace(files, "./data/", "")) %>% 
  mutate(files = str_replace(files, ".csv", "")) %>% 
  mutate(group = str_detect(files, "con")) %>% 
  mutate(group = ifelse(group == TRUE, "control", "experimental")) %>% 
  mutate(files = as.factor(str_replace(files, "^..._", ""))) %>% 
  rename(subject_ID = files) %>%
  gather(key = week, value = value, starts_with("week")) %>% 
  mutate(week = as.numeric(str_replace(week, "week_", "")))

study_data %>% 
  ggplot(aes(x = week, y = value, color = subject_ID)) +
  geom_line() +
  facet_grid(~group) +
  labs(
    title = "Control and Experimental Change Over Time"
  )
```

The experimental group shows a general trend of increase over time, while the control group's trend is largely static.

## Problem 2

```{r}
homicide_data <- read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")

homicide_data %>% 
  mutate(year_reported = str_sub(reported_date, 1, 4)) %>% 
  distinct(year_reported) %>% 
  arrange(as.numeric(year_reported))

homicide_data %>% 
  distinct(disposition)

```

This dataset contains information about `r nrow(homicide_data)` homicides in `r nrow(homicide_data %>% distinct(city))` U.S. cities in `r nrow(homicide_data %>% distinct(state))` states reported from 2007 to 2017. The victim's name, rage, age, and sex are reported for each homicide, as well as the status of the case (closed without arrest, closed by arrest, or open).

_Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”)._

```{r}
homicide_data %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>%
  select(city_state, disposition) %>% 
  group_by(city_state) %>%
  mutate(unsolved = ifelse(disposition == "Open/No arrest", 1, 0)) %>% 
  summarize(total = n(),
            unsolved = sum(unsolved))
```

