---
title: "Homework 5"
author: "Laura Cosgrove"
date: "11/3/2018"
output: github_document
---

## Problem 1
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r packages}
library(tidyverse)
```

```{r}

directory_base <- "./data/"
data <- tibble(files = str_c(directory_base, list.files("./data")))

data <- data %>% 
  mutate(subject_data = map(data$files, read_csv)) %>% 
  unnest() %>% 
  mutate(files = str_replace(files, "./data/", "")) %>% 
  mutate(files = str_replace(files, ".csv", "")) %>% 
  mutate(group = str_detect(files, "con")) %>% 
  mutate(group = ifelse(group == TRUE, "control", "experimental"))
```

